\documentclass[12pt]{article}
 \usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb,amsfonts,hyperref}
 
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
 
\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
%If you want to title your bold things something different just make another thing exactly like this but replace "problem" with the name of the thing you want, like theorem or lemma or whatever
 
\begin{document}
 
%\renewcommand{\qedsymbol}{\filledbox}
%Good resources for looking up how to do stuff:
%Binary operators: http://www.access2science.com/latex/Binary.html
%General help: http://en.wikibooks.org/wiki/LaTeX/Mathematics
%Or just google stuff
 
\title{Homework 1}
\author{CS307 - Peter Jones}
\maketitle
 
\begin{problem}{1}
\end{problem}
 
4.05She failed to disclose to the hospital she was advising that she was a co-owner of ImagiCorp.\\4.06She did not refuse to participate as an advisor in a situation in which she had a conflict of interest.

\pagebreak

\begin{problem}{2}
	
\end{problem}

The VW emissions scandal violated a great many of the clauses in the Software Engineering Code of Ethics. Engineers and managers are both to blame for this fiasco but it should be shown at least a subset of the clauses of the Code of Ethics that were violated.

\begin{itemize}
	\item 1.03 : The cars could not really pass appropriate tests.
	\item 1.04 : The cars did cause danger to the environment by masquerading as being much worse for the environment than as listed and this was not disclosed.
	\item 1.06 : Making the car emit less when being tested for emissions tests is the antithesis of "be fair and avoid deception".
	\item 3.03 : Failed to identify environmental issues related to work project.
	\item 5.11 : Managers failed to stop engineers from violating the code.
	\item 6.01 : VW failed to develop an organizational environment where acting ethically is favorable.
	\item 6.06 : Did not obey all laws governing their work.
	\item 6.07 : Were not accurate in the description of their work.
	\item 6.12 : Did not express concern over the violation of the code.
	\item 6.13 : Did not report the significant violation of the code to the proper authorities.
	\item 8.08 : As it took a team to create the emissions scandal, there must have been influence to violate the code.
\end{itemize}


Sources:
\begin{itemize}
	\item Volkswagen: The scandal explained: \url{http://www.bbc.com/news/business-34324772}
	\item Volkswagen executive pleads guilty in emissions scandal: \url{http://www.latimes.com/business/la-fi-hy-volkswagen-emissions-guilty-20170804-story.html}
	\item Everything You Need to Know about the VW Diesel-Emissions Scandal: \url{http://blog.caranddriver.com/everything-you-need-to-know-about-the-vw-diesel-emissions-scandal/}
	\item What really happened at VW: \url{https://www.economist.com/news/books-and-arts/21722818-why-emissions-scandal-still-hangs-over-german-carmaker-what-really-happened-vw}
	\item Why Volkswagen’s Emissions Scandal Has No End: \url{http://fortune.com/2017/01/11/volkswagen-emissions-scandal-2/}
\end{itemize}
 
 
 
 
\end{document}